Immutable Source-Mapped Abstract Syntax Tree:\ \, \\ A Design Pattern for Refactoring Engine APIs

### 2017-09-27 paper.tex
Added a statement of application
Clarified rewriter

@@

    \item Rewriter: \textit{Provide an API that allows clients to specify what changes
        they want to make in terms of AST nodes.}  This API can then translate these into string edits.  For example, an API might offer a \textit{Rewriter} 
class. The client would inform the \textit{Rewriter} that it wants to 
effectively delete a particular \textit{FieldDeclaration} node from the AST:
\textit{rewriter.delete(field)}.  When it is ready to manipulate the source
code, it delegates this task to the rewriter:
\textit{rewriter.rewrite(sourceCode)}.  This allows multiple edits to be made 
without conflicting with each other. This is illustrated in
Figure~\ref{fig:seq-diagram}.  The Eclipse Java and C/C++ Development
Tools~\cite{cdt-refactoring} take this approach (with slightly different class
and method names).

>>>>

Abstract syntax trees have many applications, but these two restrictions are
unique to refactorings and require a pattern that specifically addresses them.

@@

    \item Rewriter: \textit{Provide an API that allows clients to specify what changes
        they want to make in terms of AST nodes.}  This API can then translate these into string edits.  For example, an API might offer a \textit{Rewriter} 
class. The client would inform the \textit{Rewriter} that it wants to 
effectively delete a particular \textit{FieldDeclaration} node from the AST:
\textit{rewriter.delete(field)}.  The collection of planned edits can be 
        maintained by the rewriter, which handles all source-AST mapping concerns. When the client is ready to manipulate the source
code, it delegates this task to the rewriter:
\textit{rewriter.rewrite(sourceCode)}.  This allows multiple edits to be made 
without conflicting with each other. This is illustrated in
Figure~\ref{fig:seq-diagram}.  The Eclipse Java and C/C++ Development
Tools~\cite{cdt-refactoring} take this approach (with slightly different class
and method names).
